### 2019-02-25 implementation.tex
example in progress

>>>>

\begin{figure}
\begin{code}
@import storage
\vspace{0.1in}
init: storage.init()
\vspace{0.1in}
pool: <int> 5
\vspace{0.1in}
<int> := <[-10..10]>
<int> := storage.getNewVal()
{KeyError,ValueError} storage.store(<int>)
\vspace{0.1in}
property: len(storage.contents()) == len(set(storage.contents()))
\end{code}
\caption{TSTL harness for Python library with (independent) vertical and
  horizonal nondeterminisms}
\label{fig:simpleexample}
\end{figure}

\begin{figure}
\begin{code}
import random

storage = []

def contents():
    global storage
    return storage

def init():
    global storage
    storage = []

def store(n):
    global storage
    if n in storage:
       raise KeyError
    storage.append(n)
    if n < 0:
       raise ValueError

def getNewVal():
    global storage
    if len(storage) >= 1:
        bot = min(storage)
        top = max(storage)
    else:
        bot = -10
        top = 10
    v = random.randint(bot-1,top+1)
    while v in storage:
        v = random.randint(bot-1,top+1)
    return v
\end{code}
\caption{Code for Python library with (independent) vertical and
  horizonal nondeterminisms}
\label{fig:simpleexample}
\end{figure}

Figure \ref{fig:simpleexample} shows a self-contained example of a
Python program and test harness with both vertical and horizontal nondeterminism.
